---
title: "Experiment"
output:
  github_document:
    toc: yes
    toc_depth: 3
    dev: ["svg", "cairo_pdf"]
---

# Description


# Results

```{r setup, message = FALSE}

library(tidyverse)
theme_set(theme_bw())
library(knitr)
library(forcats)
library(data.table)
library(cowplot)
library(gghighlight)
library(zoo)
library(RColorBrewer)
library(stringr)
library(fBasics)
library(here)
here::i_am("./Results.rmd")

saveplot <- function(filename, ...) {
  ggsave2(filename, ...)
  knitr::plot_crop(filename)
}

traces_replays <- list.files(".", pattern="[0-9]+-trace-[a-z]+-mq[23p]-16m-replay-n[0-9]")

to_human_name <- function(name) {
  if (str_split_i(name, "-", 4) == "mq3") {
    "MQ3"
  } else if (str_split_i(name, "-", 4) == "mqp") {
    "MQP"
  } else if (str_split_i(name, "-", 4) == "mq2") {
    "MQ2"
  } else {
    name
  }
}
```

## Data Loading


```{r}
pattern <- c(month="-?\\d+", "-", day="-?\\d+", "\\s+", hour="-?\\d+", ":", minute="-?\\d+", ":", second="-?\\d+", "\\.", millisecond="-?\\d+", "\\s+", pid="-?\\d+", "\\s+", tid="-?\\d+", "\\s+", level="\\w", "\\s+VrApi\\s+:\\s+FPS=",fps_render="-?\\d+", "/", fps_refresh="-?\\d+", ",Prd=", prd="-?\\d+", "ms,Tear=", tear="-?\\d+", ",Early=", early="-?\\d+", ",Stale=", stale="-?\\d+", ",Stale2/5/10/max=", stale2="-?\\d+", "/", stale5="-?\\d+", "/", stale10="-?\\d+", "/", stalemax="-?\\d+", ",VSnc=", vsnc="-?\\d+", ",Lat=", lat="-?-?\\d+", ",Fov=", fov="-?\\d+\\w*", ",CPU", cpun="\\d", "/GPU=", cpu_level="-?\\d+", "/", gpu_level="-?\\d+", ",", cpu_freq="-?\\d+", "/", gpu_freq="-?\\d+", "MHz,OC=", oc=".+", ",TA=", ta_atw="-?\\d+\\w*", "/", ta_main="-?\\d+\\w*", "/", ta_render="-?\\d+\\w*", ",SP=", sp_atw="\\w", "/", sp_main="\\w", "/", sp_render="\\w", ",Mem=", mem="-?\\d+", "MHz,Free=", free="-?\\d+", "MB,PLS=", pls="-?\\d+", ",Temp=", temp_bat="-?\\d+\\.\\d+", "C/", temp_sens="-?\\d+\\.\\d+", "C,TW=", tw="-?\\d+\\.\\d+", "ms,App=", app="-?\\d+\\.\\d+", "ms,GD=", gd="-?\\d+\\.\\d+", "ms,CPU&GPU=", cpu_gpu="-?\\d+\\.\\d+", "ms,LCnt=", lcnt="-?\\d+", "\\(DR", dr="-?\\d+", ",LM", lm="-?\\d+", "\\),GPU%=", gpu_percent="-?\\d+\\.\\d+", ",CPU%=", cpu_percent="-?\\d+\\.\\d+", "\\(W", cpu_percent_worst="-?\\d+\\.\\d+", "\\),DSF=", dsf="-?\\d+\\.\\d+", ",CFL=", cfl_min="-?\\d+\\.\\d+", "/", cfl_max="-?\\d+\\.\\d+", ",ICFLp95=", icflp95="-?\\d+\\.\\d+", ",LD=", ld="-?\\d+", ",SF=", sf="-?\\d+\\.\\d+", ",LP=", lp="-?\\d+", ",DVFS=", dvfs="-?\\d+")

data_logcat_vrapi <- NULL
for (f in traces_replays) {
  data_logcat_vrapi <- readLines(here(f, "logcat_VrApi.log")) %>%
    tibble(line = .) %>%
    mutate(game = str_split_i(f, "-", 3)) %>%
    mutate(i = str_split_i(f, "-", -1) %>% str_split_i("n", 2)) %>%
    filter(grepl("^.+\\s+VrApi\\s+:\\s+FPS=", line)) %>%
    separate_wider_regex(line, pattern) %>%
    mutate(ts = as.numeric(second) + (60*as.numeric(minute)) + (60*60*as.numeric(hour))) %>%
    mutate(ts = ts - min(ts)) %>%
    mutate(cpu_util = 100 * as.numeric(cpu_percent)) %>%
    mutate(cpu_freq_rel = (as.numeric(cpu_freq) - min(as.numeric(cpu_freq))) / max(as.numeric(cpu_freq))) %>%
    rowwise() %>%
    mutate(cpu_freq_rel = max(0.01, cpu_freq_rel)) %>%
    ungroup() %>%
    mutate(cpu_usage_ltp = as.numeric(cpu_level) * as.numeric(cpu_percent)) %>%
    mutate(cpu_usage_ftp = as.numeric(cpu_freq) * as.numeric(cpu_percent)) %>%
    mutate(cpu_usage_ftp_rel = as.numeric(cpu_freq_rel) * as.numeric(cpu_percent)) %>%
    mutate(cpu_util_worst = 100 * as.numeric(cpu_percent_worst)) %>%
    mutate(gpu_util = 100 * as.numeric(gpu_percent)) %>%
    mutate(gpu_usage_ltp = as.numeric(gpu_level) * as.numeric(gpu_percent)) %>%
    mutate(gpu_usage_ftp = as.numeric(gpu_freq) * as.numeric(gpu_percent)) %>%
    mutate(config = f) %>%
    bind_rows(data_logcat_vrapi, .)
}
data_logcat_vrapi <- data_logcat_vrapi %>%
  type.convert(as.is = TRUE) %>%
  mutate(config = map_chr(config, to_human_name))
```


```{r}
#Inter-|   Receive                                                |  Transmit
# face |bytes    packets errs drop fifo frame compressed multicast|bytes    packets errs drop fifo colls carrier compressed
#  wlan0: 334462961  517107    0    0    0     0          0         0 110016326  375001    0    0    0     0       0          0
pattern <- c("\\s+wlan0:\\s+", rx_bytes="\\d+", "\\s+", rx_packets="\\d+", "\\s+", rx_errs="\\d+", "\\s+", rx_drop="\\d+", "\\s+", rx_fifo="\\d+", "\\s+", rx_frame="\\d+", "\\s+", rx_compressed="\\d+", "\\s+", rx_multicast="\\d+", "\\s+", tx_bytes="\\d+", "\\s+", tx_packets="\\d+", "\\s+", tx_errs="\\d+", "\\s+", tx_drop="\\d+", "\\s+", tx_fifo="\\d+", "\\s+", tx_colls="\\d+", "\\s+", tx_carrier="\\d+", "\\s+", tx_compressed="\\d+")

data_net_dev <- NULL
for (f in traces_replays) {
  data_net_dev <- readLines(here(f, "net_dev.log")) %>%
    tibble(line = .) %>%
    mutate(game = str_split_i(f, "-", 3)) %>%
    mutate(i = str_split_i(f, "-", -1) %>% str_split_i("n", 2)) %>%
    filter(grepl("^\\s+wlan0:\\s+", line)) %>%
    separate_wider_regex(line, pattern) %>%
    mutate(ts = 0:(n() - 1)) %>%
    select(ts, everything()) %>%
    mutate(config = f) %>%
    bind_rows(data_net_dev, .)
}
data_net_dev <- data_net_dev %>%
  type.convert(as.is = TRUE) %>%
  mutate(config = map_chr(config, to_human_name)) %>%
  group_by(config, game, i) %>%
  mutate(bps_tx = 8 * (tx_bytes - lag(tx_bytes))) %>%
  mutate(kbps_tx = bps_tx / 1000) %>%
  mutate(Mbps_tx = bps_tx / 1000000) %>%
  mutate(Gbps_tx = bps_tx / 1000000000) %>%
  mutate(bps_rx = 8 * (rx_bytes - lag(rx_bytes))) %>%
  mutate(kbps_rx = bps_rx / 1000) %>%
  mutate(Mbps_rx = bps_rx / 1000000) %>%
  mutate(Gbps_rx = bps_rx / 1000000000) %>%
  drop_na() %>%
  ungroup()
```

## Evolution of Hardware

### Frames per Second

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = fps_render, color = config)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

```{r, fig.width = 9, fig.height = 2.7}
data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = fps_render)) +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1) + 
  facet_grid(cols = vars(game), rows = vars(config))
```

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  # filter(ts >= start_time & ts <= end_time) %>%
  ggplot(aes(x = fps_render, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "Frames per second", y = "VR Device") +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

### Frame Time

```{r, fig.width = 9, fig.height = 2.7}
data_logcat_vrapi %>%
  filter(ts > 60) %>%
  ggplot(aes(x = ts, y = app)) +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1) + 
  facet_grid(cols = vars(game), rows = vars(config))
```

```{r, fig.width = 6, fig.height = 2}
data_logcat_vrapi %>%
  filter(ts > 60) %>%
  ggplot(aes(x = app, y = config)) +
  geom_boxplot() +
  geom_vline(xintercept = 11.1, color = "orange") +
  geom_vline(xintercept = 13.9, color = "red") +
  xlim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  labs(x="Frame time [ms]", y="VR Device") +
  facet_grid(cols = vars(game))
```

### CPU

```{r}
p <- data_logcat_vrapi %>%
  # filter(ts >= start_time & ts <= end_time) %>%
  ggplot(aes(x = cpu_util, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "CPU utilization [%]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = cpu_level, color = config)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2.7}
 data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = cpu_level)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1) + 
  facet_grid(cols = vars(game), rows = vars(config))
```


```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = cpu_freq, color = config)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2.7}
 data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = cpu_freq)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1) + 
  facet_grid(cols = vars(game), rows = vars(config))
```

```{r}
p <- data_logcat_vrapi %>%
  # filter(ts >= start_time & ts <= end_time) %>%
  ggplot(aes(x = cpu_usage_ftp, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "CPU usage [fxp]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = cpu_usage_ftp_rel, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "CPU usage [fxpr]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

```{r}
p <- data_logcat_vrapi %>%
  # filter(ts >= start_time & ts <= end_time) %>%
  ggplot(aes(x = cpu_usage_ltp, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "CPU usage [lxp]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

### GPU

```{r}
p <- data_logcat_vrapi %>%
  # filter(ts >= start_time & ts <= end_time) %>%
  ggplot(aes(x = gpu_util, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "GPU utilization [%]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```


```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = gpu_level, color = config)) +
  # geom_vline(xintercept = start_time, color = "black") +
  # geom_vline(xintercept = end_time, color = "black") +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2.7}
data_logcat_vrapi %>%
  ggplot(aes(x = ts, y = gpu_level)) +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1) +
  facet_grid(cols = vars(game), rows = vars(config))
```

```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = gpu_usage_ftp, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "GPU usage [fxp]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

```{r}
p <- data_logcat_vrapi %>%
  ggplot(aes(x = gpu_usage_ltp, y = config)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "GPU usage [lxp]", y = "VR Device") +
  theme_half_open() +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 9, fig.height = 2}
p + facet_grid(cols = vars(game))
```

### Battery Usage

```{r}
data_battery <- NULL
for (f in traces_replays) {
  data_battery <- system(paste('grep -Po "(?<=level: )[0-9]+"', here(f, "battery.log")), intern = TRUE) %>%
    tibble(battery = .) %>%
    mutate(game = str_split_i(f, "-", 3)) %>%
    mutate(battery = as.numeric(battery)) %>%
    mutate(ts = 0:(n() - 1)) %>%
    select(ts, everything()) %>%
    mutate(config = f) %>%
    bind_rows(data_battery, .)
}
data_battery <- data_battery %>%
  mutate(config = map_chr(config, to_human_name))
```

```{r}
colors <- RColorBrewer::brewer.pal(3, "Greens")[2:3]

p <- data_battery %>%
  group_by(config) %>%
  mutate(ts = ts - min(ts)) %>%
  mutate(ts = ts / 60) %>%
  filter(config != "Wired") %>%
  # mutate(rel_battery = battery + 100 - max(battery)) %>%
  ggplot(aes(x = ts, y = battery, color = config)) +
  geom_line() +
  theme_half_open() +
  background_grid() +
  theme(legend.position = c(0.05, 0.40)) +
  ylim(0, NA) +
  labs(x = "Time [m]", y = "Battery charge") +
  scale_color_manual(name = "Config", values = colors)
```

```{r, fig.width = 3, fig.height = 2}
p
```

```{r, fig.width = 5, fig.height = 2.7}
data_battery %>%
  group_by(config) %>%
  mutate(ts = ts - min(ts)) %>%
  mutate(ts = ts / 60) %>%
  filter(config != "Wired") %>%
  # mutate(rel_battery = battery + 100 - max(battery)) %>%
  ggplot(aes(x = ts, y = battery)) +
  geom_line() +
  theme_half_open() +
  background_grid() +
  theme(legend.position = c(0.05, 0.40)) +
  ylim(0, NA) +
  labs(x = "Time [m]", y = "Battery charge") +
  scale_color_manual(name = "Config", values = colors) +
  facet_grid(cols = vars(game), rows = vars(config))
```

### Network Use

```{r, fig.width = 9, fig.height = 2.7}
data_net_dev %>%
  mutate(kbps = 8 * (rx_bytes - lag(rx_bytes)) / 1000) %>%
  # filter(game != "explorevr") %>%
  drop_na() %>%
  group_by(game, config, i) %>%
  slice(2:n()) %>%
  ungroup() %>%
  ggplot(aes(x = ts, y = kbps, color = i)) +
  geom_line() +
  xlim(0, NA) +
  coord_cartesian(ylim=c(0, 1200)) +
  labs(x = "Bytes received [kbps]", y = "Setup") +
  facet_grid(cols = vars(game), rows = vars(config))
```

```{r, fig.width = 9, fig.height = 2}
data_net_dev %>%
  group_by(game, config, i) %>%
  mutate(kbps = 8 * (rx_bytes - lag(rx_bytes)) / 1000) %>%
  drop_na() %>%
  ungroup() %>%
  ggplot(aes(x = kbps, y = config)) +
  geom_boxplot() +
  coord_cartesian(xlim=c(0, 1200)) +
  labs(x = "Bytes received [kbps]", y = "Setup") +
  facet_grid(cols = vars(game))
```

## Performance Variability

### Local Apps

#### Gorilla Tag

##### Frames

The plot below clearly shows the initialization phase of the experiment run.
Every shade of blue is one run.
In each run, the number of frames per second drops to zero for a brief moment,
before maintaining constant good performance
These first few seconds are typically spent in a loading screen, and do not
reflect the performance of the system as experienced by the user.
Therefore, it makes sense to cut out the first few seconds of the experiments
in most plots.

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts < 60) %>%
  ggplot(aes(x = ts, y = fps_render, group = i, color = i)) +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "none") +
  labs(x = "Time [s]", y = "Frame time [ms]  ")
```

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = fps_render, group = i, y = i)) +
  geom_boxplot() +
  xlim(0, NA) +
  labs(x = "Frames per second", y = "Iteration") +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  scale_color_viridis_d(begin = 0.3, direction = -1)
```

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = app, group = i, y = i)) +
  geom_boxplot() +
  geom_vline(xintercept = 11.1, color = "orange", linetype = "dashed") +
  geom_vline(xintercept = 13.9, color = "red") +
  xlim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "bottom") +
  labs(x="Frame time [ms]", y="Iteration")
```

##### GPU

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = gpu_util, group = i, y = i)) +
  geom_boxplot() +
  xlim(0, 100) +
  labs(x = "GPU utilization [%]", y = "Iteration") +
  theme_half_open() +
  background_grid()
```

##### CPU

```{r, fig.width = 3, fig.height = 2}
data_logcat_vrapi %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = cpu_util, group = i, y = i)) +
  geom_boxplot() +
  xlim(0, 100) +
  labs(x = "CPU utilization [%]", y = "Iteration") +
  theme_half_open() +
  background_grid()
```

##### Network

Variability of network usage.

```{r, fig.width = 4, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = kbps_rx, y = i, group = i)) +
  geom_boxplot() +
  labs(x = "Bytes received [kbps]", y = "Iteration") +
  theme_half_open() +
  background_grid() +
  coord_cartesian(xlim=c(0, 1200), clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.5,0,0, "cm"))
```

```{r, fig.width = 4, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(x = Mbps_tx, y = i, group = i)) +
  geom_boxplot() +
  labs(x = "Bytes sent [Mbps]", y = "Iteration") +
  theme_half_open() +
  background_grid() +
  coord_cartesian(xlim=c(0, NA), clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.5,0,0, "cm"))
```

```{r, fig.width = 3, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(kbps_rx, group = i, color=i)) +
  stat_ecdf(geom = "step", pad = FALSE) +
  labs(x = "Bytes received [kbps]", y = "Fraction") +
  theme_half_open() +
  coord_cartesian(clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.4,0,0, "cm")) +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot() +
  stat_ecdf(aes(x = kbps_rx, y = log10(1 - after_stat(y)), group = i, color = i), pad=FALSE) +
  scale_y_continuous(breaks = seq(-3, 0), 
                     labels = 10^(seq(-3, 0)),
                     limits = c(-3, 0)) +
  labs(x = "Bytes received [kbps]", y = "Fraction") +
  theme_half_open() +
  coord_cartesian(clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.4,0,0, "cm")) +
  background_grid()
```

```{r}
 # test_data <- data_net_dev %>%
 #   mutate(kbps = 8 * (rx_bytes - lag(rx_bytes)) / 1000) %>%
 #   drop_na() %>%
 #   filter(game == "gorillatag")
 # test_data %>% filter(i== "n1") %>% pull(kbps)
 # 
 # ks2Test(rnorm(6000), 5+runif(6000))
 # 
 # ks2Test(test_data %>% filter(i== "n4") %>% pull(kbps), test_data %>% filter(i == "n3") %>% pull(kbps))
```


```{r, fig.width = 3, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot(aes(Mbps_tx, group = i, color=i)) +
  stat_ecdf(geom = "step", pad = FALSE) +
  labs(x = "Bytes sent [Mbps]", y = "Fraction") +
  theme_half_open() +
  coord_cartesian(clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.4,0,0, "cm")) +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  filter(ts > 60) %>%
  ggplot() +
  stat_ecdf(aes(x = Mbps_tx, y = log10(1 - after_stat(y)), group = i, color = i), pad=FALSE) +
  scale_y_continuous(breaks = seq(-3, 0), 
                     labels = 10^(seq(-3, 0)),
                     limits = c(-3, 0)) +
  labs(x = "Bytes sent [Mbps]", y = "Fraction") +
  theme_half_open() +
  coord_cartesian(clip="off") +
  theme(legend.position = "none", plot.margin=margin(0,.4,0,0, "cm")) +
  background_grid()
```

```{r, fig.width = 3, fig.height = 2}
data_net_dev %>%
  filter(game == "gorillatag") %>%
  filter(config == "MQ3") %>%
  ggplot(aes(x = ts, y = Mbps_tx, group = i, color = i)) +
  geom_line() +
  ylim(0, NA) +
  theme_half_open() +
  background_grid() +
  theme(legend.position = "none") +
  labs(x = "Time [s]", y = "Bytes sent [Mbps]    ")
```